Ornaments as indicators of social changes and cultural practices in northeastern Taiwan before and after European colonial period

### 2019-12-12 analysis/paper/paper.Rmd
updates to C14 table

```{r C14-table-data}
table_kw_dates <-
  kw_dates %>% 
  mutate(`Lab code` = str_remove(`Lab code`, " ")) %>% 
  mutate(`Above mean sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>%
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  left_join(kw_age_cali_df_tidy, "Pit-Layer") %>% 
  mutate(ave = (`2.5%` + `97.5%`)/ 2) %>% 
  mutate(ave = ifelse(is.na(ave), 200, ave)) %>%  
  arrange(ave) %>% 
  dplyr::select(`Lab code`, `Pit-Layer`, 
                `Above mean sea level (cm)`, 
                `Date BP`, 
                `Calibrated date (95% conf. level)`, 
                Context) %>% 
  mutate(`Calibrated date (95% conf. level)` = 
           ifelse(is.na(`Calibrated date (95% conf. level)`), 
                  "", 
                  `Calibrated date (95% conf. level)`))

kableExtra::kable(table_kw_dates,
             caption = "Radiocarbon ages from charcoal samples excavated from Kiwulan (Chen 2007), calibrated using IntCal13 Atmospheric curve. The codes in the context column refer to the excavator's numbering system, cf. ADD CITATION TO THE REPORT HERE")
```

>>>>

```{r C14-table-data}
# column names should follow Radiocarbon journal style:  https://www-cambridge-org.offcampus.lib.washington.edu/core/journals/radiocarbon/information/instructions-contributors

table_kw_dates <-
  kw_dates %>% 
  mutate(`Lab code` = str_remove(`Lab code`, " "),
         `Uncalibrated Age BP` = `Date BP`) %>% 
  mutate(`Above mean sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>%
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  left_join(kw_age_cali_df_tidy, "Pit-Layer") %>% 
  mutate(ave = (`2.5%` + `97.5%`)/ 2) %>% 
  mutate(ave = ifelse(is.na(ave), 200, ave)) %>%  
  arrange(ave) %>% 
  mutate(`Calibrated Age BP (95% credible interval)` = 
           ifelse(is.na(`Calibrated date (95% conf. level)`), 
                  "", 
                  `Calibrated date (95% conf. level)`)) %>% 
  mutate(`Uncalibrated Age BP` = str_remove_all(`Uncalibrated Age BP`, "yr")) %>% 
  dplyr::select(`Lab code`, 
                `Pit-Layer`, 
                `Above mean sea level (cm)`, 
                `Uncalibrated Age BP`, 
                `Calibrated Age BP (95% credible interval)`, 
                Context)

kableExtra::kable(table_kw_dates,
             caption = "Radiocarbon ages from charcoal samples excavated from Kiwulan (Chen 2007), calibrated using IntCal13 Atmospheric curve. The codes in the context column refer to the excavator's feature labels, cf. ADD CITATION TO THE REPORT HERE")
```
